|

### 2025-01-31 doc/paper.qmd
final paper

# Conclusion {#sec-conclusion}
This project effectively demonstrates the use of a systematic and collaborative workflow for empirical accounting research, leveraging the TRR 266 Template for Reproducible Empirical Accounting Research. By following an open science approach, I aimed to replicate key tables and figures from @ball_how_2008, providing insights into how earnings announcements contribute to price formation and market efficiency. While exact replications often yield different samples and outcomes due to dataset updates or methodological variations, my results align closely with the statistics presented in the original study, reinforcing the reliability of the replication process. Moreover, by extending the analysis beyond the original study’s U.S. market focus, the project highlights how market structures and investor behaviors influence the informativeness of earnings disclosures in different jurisdictions.

>>>>

# Conclusion {#sec-conclusion}
This project effectively demonstrates the use of a systematic and collaborative workflow for empirical accounting research, leveraging the TRR 266 Template for Reproducible Empirical Accounting Research. By following an open science approach, I aimed to replicate key tables and figures from @ball_how_2008, providing insights into how earnings announcements contribute to price formation and market efficiency. By extending the analysis beyond the original study’s U.S. market focus, the project highlights how market structures and investor behaviors influence the informativeness of earnings disclosures in different jurisdictions.
